Semi-inclusive deep-inelastic scattering in Wandzura--Wilczek-type approximation

### 2019-05-02 arxiv2/test-WW-type-v2H.tex
AP

The definition of the asymmetry used by the JLab experiment \cite{Avakian:2010ae} is
\be\label{Eq:ALLy}
	A_{LL,\la y\ra}(x,z,\Phperp)
	= \la p_2 \,A_{LL}(x,z,\Phperp) \ra \,
	= \frac{\la y (2-y) \; F_{LL}(x,z,\Phperp)\ra}
	{\la(1+(1-y)^2) \; F_{UU}(x,z,\Phperp)\ra} \, ,
\ee
where $p_2 = y (2-y)/(1+(1-y)^2)$ and averaging (separately in numerator
and denominator) over the kinematics of \cite{Avakian:2010ae} is implied.
We use the lattice data \cite{Hagler:2009mb} to
constrain the Gaussian width $\la\kperp^2\ra_{g_1}$ as described in
App.~\ref{App:basis-g1}. All other ingredients in (\ref{Eq:ALLy}) are known
and tested through other observables in Sec.~\ref{Sec-5.1:FUU-basis}.
Therefore the comparison of our results to the JLab data \cite{Avakian:2010ae}
shown in Fig.~\ref{jlab_ALL} provides several important tests.
First, the JLab data \cite{Avakian:2010ae} are compatible
with the Gaussian Ansatz within uncertainties. Second, the lattice
results---in the way we use them in App.~\ref{App:basis-g1}---give an 
appropriate description of the data.
	(Another important test was already presented in
	\cite{Avakian:2010ae}: the $\Phperp$--integrated (``collinear'')
	asymmetry (\ref{Eq:FLL}) is compatible with data
	from other experiments and theoretical results obtained from
	parametrizations of $f_1^a(x)$, $g_1^a(x)$, $D_1^a(z)$. This
	shows that in the pre-12~GeV era one was, to a good
	approximation, indeed already probing DIS \cite{Avakian:2010ae}.)
\bp{We remark that HERMES and COMPASS data also show flat 
$P_{hT}$-distributions \cite{Airapetian:2018rlq,Adolph:2016vou}.}

@@

\bibliography{\BibPath/biblio_ww}

>>>>

The definition of the asymmetry used by the JLab experiment \cite{Avakian:2010ae} is
\be\label{Eq:ALLy}
	A_{LL,\la y\ra}(x,z,\Phperp)
	= \la p_2 \,A_{LL}(x,z,\Phperp) \ra \,
	= \frac{\la y (2-y) \; F_{LL}(x,z,\Phperp)\ra}
	{\la(1+(1-y)^2) \; F_{UU}(x,z,\Phperp)\ra} \, ,
\ee
where $p_2 = y (2-y)/(1+(1-y)^2)$ and averaging (separately in numerator
and denominator) over the kinematics of \cite{Avakian:2010ae} is implied.
We use the lattice data \cite{Hagler:2009mb} to
constrain the Gaussian width $\la\kperp^2\ra_{g_1}$ as described in
App.~\ref{App:basis-g1}. All other ingredients in (\ref{Eq:ALLy}) are known
and tested through other observables in Sec.~\ref{Sec-5.1:FUU-basis}.
Therefore the comparison of our results to the JLab data \cite{Avakian:2010ae}
shown in Fig.~\ref{jlab_ALL} provides several important tests.
First, the JLab data \cite{Avakian:2010ae} are compatible
with the Gaussian Ansatz within uncertainties. Second, the lattice
results---in the way we use them in App.~\ref{App:basis-g1}---give an 
appropriate description of the data.
	(Another important test was already presented in
	\cite{Avakian:2010ae}: the $\Phperp$--integrated (``collinear'')
	asymmetry (\ref{Eq:FLL}) is compatible with data
	from other experiments and theoretical results obtained from
	parametrizations of $f_1^a(x)$, $g_1^a(x)$, $D_1^a(z)$. This
	shows that in the pre-12~GeV era one was, to a good
	approximation, indeed already probing DIS \cite{Avakian:2010ae}.)
We remark that HERMES and COMPASS data also show flat 
$P_{hT}$-distributions \cite{Airapetian:2018rlq,Adolph:2016vou}.

@@

\providecommand{\href}[2]{#2}\begingroup\raggedright\begin{thebibliography}{100}

\bibitem{Kotzinian:1994dv}
A.~Kotzinian, \emph{{New quark distributions and semiinclusive
  electroproduction on the polarized nucleons}},
  \href{http://dx.doi.org/10.1016/0550-3213(95)00098-D}{\emph{Nucl. Phys.} {\bf
  B441} (1995) 234--248}, [\href{https://arxiv.org/abs/hep-ph/9412283}{{\tt
  hep-ph/9412283}}].

\bibitem{Mulders:1995dh}
P.~J. Mulders and R.~D. Tangerman, \emph{{The complete tree-level result up to
  order 1/Q for polarized deep-inelastic leptoproduction}},
  \href{http://dx.doi.org/10.1016/0550-3213(95)00632-X}{\emph{Nucl. Phys.} {\bf
  B461} (1996) 197--237}, [\href{https://arxiv.org/abs/hep-ph/9510301}{{\tt
  hep-ph/9510301}}].

\bibitem{Boer:1997nt}
D.~Boer and P.~J. Mulders, \emph{{Time-reversal odd distribution functions in
  leptoproduction}},
  \href{http://dx.doi.org/10.1103/PhysRevD.57.5780}{\emph{Phys. Rev.} {\bf D57}
  (1998) 5780--5786}, [\href{https://arxiv.org/abs/hep-ph/9711485}{{\tt
  hep-ph/9711485}}].

\bibitem{Goeke:2005hb}
K.~Goeke, A.~Metz and M.~Schlegel, \emph{{Parameterization of the quark--quark
  correlator of a spin-1/2 hadron}},
  \href{http://dx.doi.org/10.1016/j.physletb.2005.05.037}{\emph{Phys. Lett.}
  {\bf B618} (2005) 90--96}, [\href{https://arxiv.org/abs/hep-ph/0504130}{{\tt
  hep-ph/0504130}}].

\bibitem{Bacchetta:2006tn}
A.~Bacchetta, M.~Diehl, K.~Goeke, A.~Metz, P.~J. Mulders and M.~Schlegel,
  \emph{{Semi-inclusive deep inelastic scattering at small transverse
  momentum}},
  \href{http://dx.doi.org/10.1088/1126-6708/2007/02/093}{\emph{JHEP} {\bf 02}
  (2007) 093}, [\href{https://arxiv.org/abs/hep-ph/0611265}{{\tt
  hep-ph/0611265}}].

\bibitem{Stock:1994vv}
F.~Stock et~al., \emph{{The FILTEX / HERMES polarized hydrogen atomic beam
  source}}, \href{http://dx.doi.org/10.1016/0168-9002(94)90210-0}{\emph{Nucl.
  Instrum. Meth.} {\bf A343} (1994) 334--342}.

\bibitem{Airapetian:2004yf}
{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{The HERMES
  polarized hydrogen and deuterium gas target in the HERA electron storage
  ring}}, \href{http://dx.doi.org/10.1016/j.nima.2004.11.020}{\emph{Nucl.
  Instrum. Meth.} {\bf A540} (2005) 68--101},
  [\href{https://arxiv.org/abs/physics/0408137}{{\tt physics/0408137}}].

\bibitem{Crabb:1997cy}
D.~G. Crabb and W.~Meyer, \emph{{Solid polarized targets for nuclear and
  particle physics experiments}},
  \href{http://dx.doi.org/10.1146/annurev.nucl.47.1.67}{\emph{Ann. Rev. Nucl.
  Part. Sci.} {\bf 47} (1997) 67--109}.

\bibitem{Goertz:2002vv}
S.~Goertz, W.~Meyer and G.~Reicherz, \emph{{Polarized H, D and $^{3}$He targets
  for particle physics experiments}},
  \href{http://dx.doi.org/10.1016/S0146-6410(02)00159-X}{\emph{Prog. Part.
  Nucl. Phys.} {\bf 49} (2002) 403--489}.

\bibitem{Arnold:2008kf}
S.~Arnold, A.~Metz and M.~Schlegel, \emph{{Dilepton production from polarized
  hadron hadron collisions}},
  \href{http://dx.doi.org/10.1103/PhysRevD.79.034005}{\emph{Phys. Rev.} {\bf
  D79} (2009) 034005}, [\href{https://arxiv.org/abs/0809.2262}{{\tt
  0809.2262}}].

\bibitem{Metz:2016swz}
A.~Metz and A.~Vossen, \emph{{Parton fragmentation functions}},
  \href{http://dx.doi.org/10.1016/j.ppnp.2016.08.003}{\emph{Prog. Part. Nucl.
  Phys.} {\bf 91} (2016) 136--202},
  [\href{https://arxiv.org/abs/1607.02521}{{\tt 1607.02521}}].

\bibitem{Miller:2007ae}
G.~A. Miller, \emph{{Densities, parton distributions, and measuring the
  nonspherical shape of the nucleon}},
  \href{http://dx.doi.org/10.1103/PhysRevC.76.065209}{\emph{Phys. Rev.} {\bf
  C76} (2007) 065209}, [\href{https://arxiv.org/abs/0708.2297}{{\tt
  0708.2297}}].

\bibitem{Burkardt:2007rv}
M.~Burkardt, \emph{{Spin-orbit correlations and single-spin asymmetries}},  in
  \emph{{Workshop on Exclusive Reactions at High Momentum Transfer Newport
  News, Virginia, May 21-24, 2007}}, 2007.
\newblock \href{https://arxiv.org/abs/0709.2966}{{\tt 0709.2966}}.

\bibitem{Burkardt:2009rf}
M.~Burkardt, \emph{{The $g_{2}$ Structure Function}},
  \href{http://dx.doi.org/10.1063/1.3203298}{\emph{AIP Conf.Proc.} {\bf 1155}
  (2009) 26--34}, [\href{https://arxiv.org/abs/0905.4079}{{\tt 0905.4079}}].

\bibitem{Bacchetta:1999kz}
A.~Bacchetta, M.~Boglione, A.~Henneman and P.~J. Mulders, \emph{{Bounds on
  Transverse Momentum Dependent Distribution and Fragmentation Functions}},
  \href{http://dx.doi.org/10.1103/PhysRevLett.85.712}{\emph{Phys. Rev. Lett.}
  {\bf 85} (2000) 712--715}, [\href{https://arxiv.org/abs/hep-ph/9912490}{{\tt
  hep-ph/9912490}}].

\bibitem{Wandzura:1977qf}
S.~Wandzura and F.~Wilczek, \emph{{Sum rules for spin-dependent
  electroproduction: Test of relativistic constituent quarks}},
  \href{http://dx.doi.org/10.1016/0370-2693(77)90700-6}{\emph{Phys. Lett.} {\bf
  B72} (1977) 195}.

\bibitem{Jaffe:1991ra}
R.~Jaffe and X.~Ji, \emph{{Chiral-odd parton distributions and Drell--Yan
  processes}},
  \href{http://dx.doi.org/10.1016/0550-3213(92)90110-W}{\emph{Nucl. Phys.} {\bf
  B375} (1992) 527--560}.

\bibitem{Jaffe:1989xx}
R.~L. Jaffe, \emph{{$g_{2}$-The Nucleon's Other Spin-Dependent Structure
  Function}}, {\emph{Comments Nucl. Part. Phys.} {\bf 19} (1990) 239--257}.

\bibitem{Balla:1997hf}
J.~Balla, M.~V. Polyakov and C.~Weiss, \emph{{Nucleon matrix elements of
  higher-twist operators from the instanton vacuum}},
  \href{http://dx.doi.org/10.1016/S0550-3213(98)00638-5}{\emph{Nucl. Phys.}
  {\bf B510} (1998) 327--364},
  [\href{https://arxiv.org/abs/hep-ph/9707515}{{\tt hep-ph/9707515}}].

\bibitem{Dressler:1999hc}
B.~Dressler and M.~V. Polyakov, \emph{{Twist-three contribution to $h_{L}$ in
  the instanton vacuum}},
  \href{http://dx.doi.org/10.1103/PhysRevD.61.097501}{\emph{Phys. Rev.} {\bf
  D61} (2000) 097501}, [\href{https://arxiv.org/abs/hep-ph/9912376}{{\tt
  hep-ph/9912376}}].

\bibitem{Gockeler:2000ja}
M.~G{\"o}ckeler, R.~Horsley, W.~K{\"u}rzinger, H.~Oelrich, D.~Pleiter et~al.,
  \emph{{Lattice calculation of the nucleon's spin-dependent structure function
  $g_{2}$ reexamined}},
  \href{http://dx.doi.org/10.1103/PhysRevD.63.074506}{\emph{Phys. Rev.} {\bf
  D63} (2001) 074506}, [\href{https://arxiv.org/abs/hep-lat/0011091}{{\tt
  hep-lat/0011091}}].

\bibitem{Gockeler:2005vw}
M.~G{\"o}ckeler, R.~Horsley, D.~Pleiter, P.~E. Rakow, A.~Sch{\"a}fer et~al.,
  \emph{{Investigation of the second moment of the nucleon's $g_{1}$ and
  $g_{2}$ structure functions in two-flavor lattice QCD}},
  \href{http://dx.doi.org/10.1103/PhysRevD.72.054507}{\emph{Phys. Rev.} {\bf
  D72} (2005) 054507}, [\href{https://arxiv.org/abs/hep-lat/0506017}{{\tt
  hep-lat/0506017}}].

\bibitem{Abe:1998wq}
{\scshape E143} collaboration, K.~Abe et~al., \emph{{Measurements of the proton
  and deuteron spin structure functions $g_{1}$ and $g_{2}$}},
  \href{http://dx.doi.org/10.1103/PhysRevD.58.112003}{\emph{Phys. Rev.} {\bf
  D58} (1998) 112003}, [\href{https://arxiv.org/abs/hep-ph/9802357}{{\tt
  hep-ph/9802357}}].

\bibitem{Anthony:2002hy}
{\scshape E155} collaboration, P.~L. Anthony et~al., \emph{{Precision
  measurement of the proton and deuteron spin structure functions $g_{2}$ and
  asymmetries $A_{2}$}},
  \href{http://dx.doi.org/10.1016/S0370-2693(02)03015-0}{\emph{Phys. Lett.}
  {\bf B553} (2003) 18--24}, [\href{https://arxiv.org/abs/hep-ex/0204028}{{\tt
  hep-ex/0204028}}].

\bibitem{Airapetian:2011wu}
{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Measurement of
  the virtual-photon asymmetry $A_2$ and the spin-structure function $g_2$ of
  the proton}},
  \href{http://dx.doi.org/10.1140/epjc/s10052-012-1921-5}{\emph{Eur. Phys. J.}
  {\bf C72} (2012) 1921}, [\href{https://arxiv.org/abs/1112.5584}{{\tt
  1112.5584}}].

\bibitem{Kotzinian:1995cz}
A.~M. Kotzinian and P.~J. Mulders, \emph{{Longitudinal quark polarization in
  transversely polarized nucleons}},
  \href{http://dx.doi.org/10.1103/PhysRevD.54.1229}{\emph{Phys. Rev.} {\bf D54}
  (1996) 1229--1232}, [\href{https://arxiv.org/abs/hep-ph/9511420}{{\tt
  hep-ph/9511420}}].

\bibitem{Kotzinian:1997wt}
A.~M. Kotzinian and P.~J. Mulders, \emph{{Probing transverse quark polarization
  via azimuthal asymmetries in leptoproduction}},
  \href{http://dx.doi.org/10.1016/S0370-2693(97)00708-9}{\emph{Phys. Lett.}
  {\bf B406} (1997) 373--380},
  [\href{https://arxiv.org/abs/hep-ph/9701330}{{\tt hep-ph/9701330}}].

\bibitem{Kotzinian:2006dw}
A.~Kotzinian, B.~Parsamyan and A.~Prokudin, \emph{{Predictions for double spin
  asymmetry $A_{LT}$ in semiinclusive DIS}},
  \href{http://dx.doi.org/10.1103/PhysRevD.73.114017}{\emph{Phys. Rev.} {\bf
  D73} (2006) 114017}, [\href{https://arxiv.org/abs/hep-ph/0603194}{{\tt
  hep-ph/0603194}}].

\bibitem{Avakian:2007mv}
H.~Avakian et~al., \emph{{Are there approximate relations among transverse
  momentum dependent distribution functions?}},
  \href{http://dx.doi.org/10.1103/PhysRevD.77.014023}{\emph{Phys. Rev.} {\bf
  D77} (2008) 014023}, [\href{https://arxiv.org/abs/0709.3253}{{\tt
  0709.3253}}].

\bibitem{Metz:2008ib}
A.~Metz, P.~Schweitzer and T.~Teckentrup, \emph{{Lorentz invariance relations
  between parton distributions and the Wandzura--Wilczek approximation}},
  \href{http://dx.doi.org/10.1016/j.physletb.2009.08.052}{\emph{Phys. Lett.}
  {\bf B680} (2009) 141--147}, [\href{https://arxiv.org/abs/0810.5212}{{\tt
  0810.5212}}].

\bibitem{Teckentrup:2009tk}
T.~Teckentrup, A.~Metz and P.~Schweitzer, \emph{{Lorentz invariance relations
  and Wandzura--Wilczek approximation}},
  \href{http://dx.doi.org/10.1142/S0217732309001169}{\emph{Mod. Phys. Lett.}
  {\bf A24} (2009) 2950--2959}, [\href{https://arxiv.org/abs/0910.2567}{{\tt
  0910.2567}}].

\bibitem{Tangerman:1994bb}
R.~Tangerman and P.~Mulders, \emph{{Polarized twist-three distributions $g_{T}$
  and $h_{L}$ and the role of intrinsic transverse momentum}},
  \href{https://arxiv.org/abs/hep-ph/9408305}{{\tt hep-ph/9408305}}.

\bibitem{Avakian:2015vha}
H.~Avakian, H.~Matevosyan, B.~Pasquini and P.~Schweitzer, \emph{{Studying the
  information content of TMDs using Monte Carlo generators}},
  \href{http://dx.doi.org/10.1088/0954-3899/42/3/034015}{\emph{J. Phys.} {\bf
  G42} (2015) 034015}.

\bibitem{Metz:2004je}
A.~Metz and M.~Schlegel, \emph{{Twist-3 single-spin asymmetries in
  semi-inclusive deep-inelastic scattering}},
  \href{http://dx.doi.org/10.1140/epja/i2004-10050-8}{\emph{Eur. Phys. J.} {\bf
  A22} (2004) 489--494}, [\href{https://arxiv.org/abs/hep-ph/0403182}{{\tt
  hep-ph/0403182}}].

\bibitem{Gamberg:2006ru}
L.~P. Gamberg, D.~S. Hwang, A.~Metz and M.~Schlegel, \emph{{Light-cone
  divergence in twist-3 correlation functions}},
  \href{http://dx.doi.org/10.1016/j.physletb.2006.07.005}{\emph{Phys. Lett.}
  {\bf B639} (2006) 508--512},
  [\href{https://arxiv.org/abs/hep-ph/0604022}{{\tt hep-ph/0604022}}].

\bibitem{Mathematica}
A.~Prokudin and K.~Tezgin, ``{Open-source packages with implementations of
  SIDIS structure functions in the WW-type approximation are publicly available
  on \texttt{github.com}: \\ in \texttt{Mathematica, {V}ersion 11.3} on {\href{
  https://github.com/prokudin/WW-SIDIS}{
  https://github.com/prokudin/WW-SIDIS}},\\ in \texttt{Python} on {\href{
  https://jeffersonlab.github.io/jam3d/_build/html/index.html}{
  https://jeffersonlab.github.io/jam3d/\_build/html/index.html}}}.''

\bibitem{Collins:2002kn}
J.~C. Collins, \emph{{Leading-twist single-transverse-spin asymmetries:
  Drell--Yan and deep-inelastic scattering}}, {\emph{Phys. Lett.} {\bf B536}
  (2002) 43--48}, [\href{https://arxiv.org/abs/hep-ph/0204004}{{\tt
  hep-ph/0204004}}].

\bibitem{Ralston:1979ys}
J.~P. Ralston and D.~E. Soper, \emph{{Production of Dimuons from High-Energy
  Polarized Proton Proton Collisions}},
  \href{http://dx.doi.org/10.1016/0550-3213(79)90082-8}{\emph{Nucl. Phys.} {\bf
  B152} (1979) 109}.

\bibitem{Collins:1981uk}
J.~C. Collins and D.~E. Soper, \emph{{Back-To-Back Jets in QCD}},
  \href{http://dx.doi.org/10.1016/0550-3213(81)90339-4}{\emph{Nucl. Phys.} {\bf
  B193} (1981) 381}.

\bibitem{Ji:2004wu}
X.~Ji, J.-P. Ma and F.~Yuan, \emph{{QCD factorization for semi-inclusive
  deep-inelastic scattering at low transverse momentum}},
  \href{http://dx.doi.org/10.1103/PhysRevD.71.034005}{\emph{Phys. Rev.} {\bf
  D71} (2005) 034005}, [\href{https://arxiv.org/abs/hep-ph/0404183}{{\tt
  hep-ph/0404183}}].

\bibitem{Ji:2004xq}
X.~Ji, J.-P. Ma and F.~Yuan, \emph{{QCD factorization for spin-dependent cross
  sections in DIS and Drell-Yan processes at low transverse momentum}},
  \href{http://dx.doi.org/10.1016/j.physletb.2004.07.026}{\emph{Phys. Lett.}
  {\bf B597} (2004) 299--308},
  [\href{https://arxiv.org/abs/hep-ph/0405085}{{\tt hep-ph/0405085}}].

\bibitem{Collins:2011zzd}
J.~Collins, \emph{{Foundations of perturbative QCD}}, {\emph{Camb. Monogr.
  Part. Phys. Nucl. Phys. Cosmol.} {\bf 32} (2011) 1--624}.

\bibitem{Echevarria:2012js}
M.~G. Echevarr\'ia, A.~Idilbi and I.~Scimemi, \emph{{Soft and collinear
  factorization and transverse momentum dependent parton distribution
  functions}},
  \href{http://dx.doi.org/10.1016/j.physletb.2013.09.003}{\emph{Phys. Lett.}
  {\bf B726} (2013) 795--801}, [\href{https://arxiv.org/abs/1211.1947}{{\tt
  1211.1947}}].

\bibitem{Aybat:2011zv}
S.~M. Aybat and T.~C. Rogers, \emph{{TMD Parton Distribution and Fragmentation
  Functions with QCD Evolution}},
  \href{http://dx.doi.org/10.1103/PhysRevD.83.114042}{\emph{Phys. Rev.} {\bf
  D83} (2011) 114042}, [\href{https://arxiv.org/abs/1101.5057}{{\tt
  1101.5057}}].

\bibitem{Aybat:2011ge}
S.~M. Aybat, J.~C. Collins, J.-W. Qiu and T.~C. Rogers, \emph{{The QCD
  Evolution of the Sivers Function}},
  \href{http://dx.doi.org/10.1103/PhysRevD.85.034043}{\emph{Phys. Rev.} {\bf
  D85} (2012) 034043}, [\href{https://arxiv.org/abs/1110.6428}{{\tt
  1110.6428}}].

\bibitem{Echevarria:2014xaa}
M.~G. Echevarria, A.~Idilbi, Z.-B. Kang and I.~Vitev, \emph{{QCD Evolution of
  the Sivers Asymmetry}},
  \href{http://dx.doi.org/10.1103/PhysRevD.89.074013}{\emph{Phys. Rev.} {\bf
  D89} (2014) 074013}, [\href{https://arxiv.org/abs/1401.5078}{{\tt
  1401.5078}}].

\bibitem{Collins:2014jpa}
J.~Collins and T.~Rogers, \emph{{Understanding the large-distance behavior of
  transverse-momentum-dependent parton densities and the Collins-Soper
  evolution kernel}},
  \href{http://dx.doi.org/10.1103/PhysRevD.91.074020}{\emph{Phys. Rev.} {\bf
  D91} (2015) 074020}, [\href{https://arxiv.org/abs/1412.3820}{{\tt
  1412.3820}}].

\bibitem{Ma:2013aca}
J.~P. Ma and G.~P. Zhang, \emph{{QCD corrections of all structure functions in
  transverse momentum dependent factorization for Drell--Yan processes}},
  \href{http://dx.doi.org/10.1007/JHEP02(2014)100}{\emph{JHEP} {\bf 02} (2014)
  100}, [\href{https://arxiv.org/abs/1308.2044}{{\tt 1308.2044}}].

\bibitem{Aybat:2011ta}
S.~M. Aybat, A.~Prokudin and T.~C. Rogers, \emph{{Calculation of TMD Evolution
  for Transverse Single Spin Asymmetry Measurements}},
  \href{http://dx.doi.org/10.1103/PhysRevLett.108.242003}{\emph{Phys. Rev.
  Lett.} {\bf 108} (2012) 242003}, [\href{https://arxiv.org/abs/1112.4423}{{\tt
  1112.4423}}].

\bibitem{Kang:2015msa}
Z.-B. Kang, A.~Prokudin, P.~Sun and F.~Yuan, \emph{{Extraction of quark
  transversity distribution and Collins fragmentation functions with QCD
  evolution}}, \href{http://dx.doi.org/10.1103/PhysRevD.93.014009}{\emph{Phys.
  Rev.} {\bf D93} (2016) 014009}, [\href{https://arxiv.org/abs/1505.05589}{{\tt
  1505.05589}}].

\bibitem{Gutierrez-Reyes:2017glx}
D.~Gutiérrez-Reyes, I.~Scimemi and A.~A. Vladimirov, \emph{{Twist-2 matching of
  transverse momentum dependent distributions}},
  \href{http://dx.doi.org/10.1016/j.physletb.2017.03.031}{\emph{Phys. Lett.}
  {\bf B769} (2017) 84--89}, [\href{https://arxiv.org/abs/1702.06558}{{\tt
  1702.06558}}].

\bibitem{Gutierrez-Reyes:2018qez}
D.~Gutierrez-Reyes, I.~Scimemi, W.~J. Waalewijn and L.~Zoppi,
  \emph{{Transverse-Momentum-Dependent Distributions with Jets}},
  \href{http://dx.doi.org/10.1103/PhysRevLett.121.162001}{\emph{Phys. Rev.
  Lett.} {\bf 121} (2018) 162001},
  [\href{https://arxiv.org/abs/1807.07573}{{\tt 1807.07573}}].

\bibitem{Scimemi:2018mmi}
I.~Scimemi and A.~Vladimirov, \emph{{Matching of transverse momentum dependent
  distributions at twist-3}},
  \href{http://dx.doi.org/10.1140/epjc/s10052-018-6263-5}{\emph{Eur. Phys. J.}
  {\bf C78} (2018) 802}, [\href{https://arxiv.org/abs/1804.08148}{{\tt
  1804.08148}}].

\bibitem{Chen:2016hgw}
A.~P. Chen and J.~P. Ma, \emph{{Light-cone singularities and
  transverse-momentum-dependent factorization at twist-3}},
  \href{http://dx.doi.org/10.1016/j.physletb.2017.03.015}{\emph{Phys. Lett.}
  {\bf B768} (2017) 380--386}, [\href{https://arxiv.org/abs/1610.08634}{{\tt
  1610.08634}}].

\bibitem{Efremov:2002qh}
A.~V. Efremov and P.~Schweitzer, \emph{{The chirally-odd twist-3 distribution
  $e^{a}(x)$}},
  \href{http://dx.doi.org/10.1088/1126-6708/2003/08/006}{\emph{JHEP} {\bf 08}
  (2003) 006}, [\href{https://arxiv.org/abs/hep-ph/0212044}{{\tt
  hep-ph/0212044}}].

\bibitem{Jaffe:1996zw}
R.~L. Jaffe, \emph{{Spin, twist and hadron structure in deep inelastic
  processes}},  in \emph{{The spin structure of the nucleon. Proceedings,
  International School of Nucleon Structure, 1st Course, Erice, Italy, August
  3-10, 1995}}, pp.~42--129, 1996.
\newblock \href{https://arxiv.org/abs/hep-ph/9602236}{{\tt hep-ph/9602236}}.

\bibitem{Kanazawa:2015ajw}
K.~Kanazawa, Y.~Koike, A.~Metz, D.~Pitonyak and M.~Schlegel, \emph{{Operator
  constraints for twist-3 functions and Lorentz invariance properties of
  twist-3 observables}},
  \href{http://dx.doi.org/10.1103/PhysRevD.93.054024}{\emph{Phys. Rev.} {\bf
  D93} (2016) 054024}, [\href{https://arxiv.org/abs/1512.07233}{{\tt
  1512.07233}}].

\bibitem{Shuryak:1981ff}
E.~V. Shuryak, \emph{{The role of instantons in quantum chromodynamics: (I).
  Physical vacuum}},
  \href{http://dx.doi.org/10.1016/0550-3213(82)90478-3}{\emph{Nucl. Phys.} {\bf
  B203} (1982) 93}.

\bibitem{Diakonov:1983hh}
D.~Diakonov and V.~Y. Petrov, \emph{{Instanton-based vacuum from Feynman
  variational principle}},
  \href{http://dx.doi.org/10.1016/0550-3213(84)90432-2}{\emph{Nucl. Phys.} {\bf
  B245} (1984) 259}.

\bibitem{Diakonov:1995qy}
D.~Diakonov, M.~V. Polyakov and C.~Weiss, \emph{{Hadronic matrix elements of
  gluon operators in the instanton vacuum}},
  \href{http://dx.doi.org/10.1016/0550-3213(95)00675-3}{\emph{Nucl. Phys.} {\bf
  B461} (1996) 539--580}, [\href{https://arxiv.org/abs/hep-ph/9510232}{{\tt
  hep-ph/9510232}}].

\bibitem{Adams:1994id}
{\scshape Spin Muon} collaboration, D.~Adams et~al., \emph{{Spin asymmetry in
  muon-proton deep inelastic scattering on a transversely polarized target}},
  \href{http://dx.doi.org/10.1016/0370-2693(94)00968-6}{\emph{Phys. Lett.} {\bf
  B336} (1994) 125--130}, [\href{https://arxiv.org/abs/hep-ex/9408001}{{\tt
  hep-ex/9408001}}].

\bibitem{Accardi:2009au}
A.~Accardi, A.~Bacchetta, W.~Melnitchouk and M.~Schlegel, \emph{{What can break
  the Wandzura--Wilczek relation?}},
  \href{http://dx.doi.org/10.1088/1126-6708/2009/11/093}{\emph{JHEP} {\bf 11}
  (2009) 093}, [\href{https://arxiv.org/abs/0907.2942}{{\tt 0907.2942}}].

\bibitem{Gluck:1998xa}
M.~Gl{\"u}ck, E.~Reya and A.~Vogt, \emph{{Dynamical parton distributions
  revisited}}, \href{http://dx.doi.org/10.1007/s100520050289}{\emph{Eur. Phys.
  J.} {\bf C5} (1998) 461--470},
  [\href{https://arxiv.org/abs/hep-ph/9806404}{{\tt hep-ph/9806404}}].

\bibitem{Efremov:2006qm}
A.~V. Efremov, K.~Goeke and P.~Schweitzer, \emph{{Collins effect in
  semiinclusive deeply inelastic scattering and in
  electron-positron-annihilation}},
  \href{http://dx.doi.org/10.1103/PhysRevD.73.094025}{\emph{Phys. Rev.} {\bf
  D73} (2006) 094025}, [\href{https://arxiv.org/abs/hep-ph/0603054}{{\tt
  hep-ph/0603054}}].

\bibitem{Anselmino:2007fs}
M.~Anselmino et~al., \emph{{Transversity and Collins functions from SIDIS and
  $e^{+} e^{-}$ data}},
  \href{http://dx.doi.org/10.1103/PhysRevD.75.054032}{\emph{Phys. Rev.} {\bf
  D75} (2007) 054032}, [\href{https://arxiv.org/abs/hep-ph/0701006}{{\tt
  hep-ph/0701006}}].

\bibitem{Anselmino:2008jk}
M.~Anselmino et~al., \emph{{Update on transversity and Collins functions from
  SIDIS and $e^{+} e^{-}$ data}},
  \href{http://dx.doi.org/10.1016/j.nuclphysbps.2009.03.117}{\emph{Nucl. Phys.
  Proc. Suppl.} {\bf 191} (2009) 98--107},
  [\href{https://arxiv.org/abs/0812.4366}{{\tt 0812.4366}}].

\bibitem{Koike:2008du}
Y.~Koike, K.~Tanaka and S.~Yoshida, \emph{{Drell--Yan double-spin asymmetry
  $A_{LT}$ in polarized $p\bar{p}$ collisions: Wandzura--Wilczek
  contribution}},
  \href{http://dx.doi.org/10.1016/j.physletb.2008.08.049}{\emph{Phys. Lett.}
  {\bf B668} (2008) 286--292}, [\href{https://arxiv.org/abs/0805.2289}{{\tt
  0805.2289}}].

\bibitem{Hagler:2009mb}
P.~H{\"a}gler, B.~U. Musch, J.~W. Negele and A.~Sch{\"a}fer, \emph{{Intrinsic
  quark transverse momentum in the nucleon from lattice QCD}},
  \href{http://dx.doi.org/10.1209/0295-5075/88/61001}{\emph{Europhys. Lett.}
  {\bf 88} (2009) 61001}, [\href{https://arxiv.org/abs/0908.1283}{{\tt
  0908.1283}}].

\bibitem{Musch:2010ka}
B.~U. Musch, P.~H{\"a}gler, J.~W. Negele and A.~Sch{\"a}fer, \emph{{Exploring
  quark transverse momentum distributions with lattice QCD}},
  \href{http://dx.doi.org/10.1103/PhysRevD.83.094507}{\emph{Phys. Rev.} {\bf
  D83} (2011) 094507}, [\href{https://arxiv.org/abs/1011.1213}{{\tt
  1011.1213}}].

\bibitem{Alexandrou:2017dzj}
C.~Alexandrou, S.~Bacchio, K.~Cichy, M.~Constantinou, K.~Hadjiyiannakou,
  K.~Jansen et~al., \emph{{Computation of parton distributions from the
  quasi-PDF approach at the physical point}},
  \href{http://dx.doi.org/10.1051/epjconf/201817514008}{\emph{EPJ Web Conf.}
  {\bf 175} (2018) 14008}, [\href{https://arxiv.org/abs/1710.06408}{{\tt
  1710.06408}}].

\bibitem{Ishikawa:2017faj}
T.~Ishikawa, Y.-Q. Ma, J.-W. Qiu and S.~Yoshida, \emph{{Renormalizability of
  quasiparton distribution functions}},
  \href{http://dx.doi.org/10.1103/PhysRevD.96.094019}{\emph{Phys. Rev.} {\bf
  D96} (2017) 094019}, [\href{https://arxiv.org/abs/1707.03107}{{\tt
  1707.03107}}].

\bibitem{Engelhardt:2015xja}
M.~Engelhardt, P.~H{\"a}gler, B.~Musch, J.~Negele and A.~Sch{\"a}fer,
  \emph{{Lattice QCD study of the Boer-Mulders effect in a pion}},
  \href{http://dx.doi.org/10.1103/PhysRevD.93.054501}{\emph{Phys. Rev.} {\bf
  D93} (2016) 054501}, [\href{https://arxiv.org/abs/1506.07826}{{\tt
  1506.07826}}].

\bibitem{Ji:2014hxa}
X.~Ji, P.~Sun, X.~Xiong and F.~Yuan, \emph{{Soft factor subtraction and
  transverse momentum dependent parton distributions on the lattice}},
  \href{http://dx.doi.org/10.1103/PhysRevD.91.074009}{\emph{Phys. Rev.} {\bf
  D91} (2015) 074009}, [\href{https://arxiv.org/abs/1405.7640}{{\tt
  1405.7640}}].

\bibitem{Musch:2011er}
B.~U. Musch, P.~H{\"a}gler, M.~Engelhardt, J.~W. Negele and A.~Sch{\"a}fer,
  \emph{{Sivers and Boer-Mulders observables from lattice QCD}},
  \href{http://dx.doi.org/10.1103/PhysRevD.85.094510}{\emph{Phys. Rev.} {\bf
  D85} (2012) 094510}, [\href{https://arxiv.org/abs/1111.4249}{{\tt
  1111.4249}}].
